Number of COVID-19 Cases in Canada in 2022 By Region, Age, and Sex

### 2024-12-03 paper/paper.qmd
Updated formating and references

This analysis looks at COVID-19 data from 2022 in Canada and analyzes how the different population and individual-level demographic variables, such as age, sex, and region of life, influenced the risk of fatality from COVID-19. The paper uses the demographic data gathered from 2022 to predict the characteristics of populations and individuals that may be at higher risk of fatality once they have been diagnosed with COVID.

@@

I use the statistical programming language R [@citeR] to analyze the data and to create graphs and models. Th packages that were used include tidyverse [@tidyverse], tidyr [@tidyr], dplyr [@dplyr], arrow [@arrow], DataExplorer [@dataexplorer], corrplot [@corrplot], caret [@caret], and pROC [@pROC]. My data [@covid_data] was obtained from COVerAGE-DB, which was housed in Open Science Framework. The data anlysis was conducted based on the guidance of @tellingstories.

@@

```{r}
#| label: fig-model_age
#| fig-cap: Predicted probability of high risk based on age intervals. The median predicted probability of high risk is shown as a decimal, where age intervals [20, 30) and [50, 60) have relatively higher predicted probabilities of high risk. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'

@@

### Odds Ratio with Confidence Intervals

>>>>

This analysis looks at COVID-19 data from 2022 in Canada and analyzes how the different population and individual-level demographic variables, such as age, sex, and region of life, influenced the risk of fatality from COVID-19. The analysis focuses on isolating these demographic factors and examining their individual effects. The paper uses the demographic data gathered from 2022 to predict the characteristics of populations and individuals that may be at higher risk of fatality once they have been diagnosed with COVID.

@@

I use the statistical programming language R [@citeR] to analyze the data and to create graphs and models. Th packages that were used include tidyverse [@tidyverse], tidyr [@tidyr], dplyr [@dplyr], arrow [@arrow], DataExplorer [@dataexplorer], corrplot [@corrplot], caret [@caret], httr [@httr], here[@here], and pROC [@pROC]. My data [@covid_data] was obtained from COVerAGE-DB, which was housed in Open Science Framework. The data anlysis was conducted based on the guidance of @tellingstories.

@@

```{r}
#| label: fig-model_age
#| fig-cap: Predicted probability of high risk based on age intervals. The median predicted probability of high risk is shown as a decimal, where age intervals 20-30 and 50-60 have relatively higher predicted probabilities of high risk. 
#| echo: false
#| warning: false
#| message: false
#| results: 'hide'

@@

```
\newpage
### Odds Ratio with Confidence Intervals
